---
surname: Mike Mahoney
address: "" # Subhead under name 
phone: 781-812-8842
www: mm218.dev
email: "mike.mahoney.218@gmail.com"
github: mikemahoney218
linkedin: mikemahoney218
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
docname: "Curriculum Vitae"
headcolor: 414141 #08004f
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
source("make_detailed_section.R")
```

# Education

```{r education}
PHD_ESF_Current <- vector("list")
PHD_ESF_Current$Details <- c("Doctor of Philosophy in Environmental Science (Area of Study: Coupled Natural and Human Systems)", 
                       "August 2020 - Present", 
                       "State University of New York College of Environmental 
                       Science and Forestry (SUNY-ESF)", 
                       "Syracuse, New York")
PHD_ESF_Current$Bullets <- NA

BS_ESF_18 <- vector("list")
BS_ESF_18$Details <- c("Bachelor of Science with Honors magna cum laude in 
                       Forest Ecosystem Science (GPA: 3.723)", 
                       "December 2018", 
                       "State University of New York College of Environmental 
                       Science and Forestry (SUNY-ESF)", 
                       "Syracuse, New York")
BS_ESF_18$Bullets <- c("Thesis: Beaver Foraging Preferences and Impacts on 
                       Forest Structure in New York’s Adirondack Mountains")

make_detailed_section(PHD_ESF_Current, order = 1:4)
#make_detailed_section(BS_ESF_18, order = 1:4)
```

```{r eval=FALSE}
# Professional Appointments
# (tenure-track, instructorships, postdocs)
# Institution, department, title, year
```


# Publications

\vspace{0.2cm}

## In Review

```{r eval = TRUE}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2023", "", "Mahoney, M. J.", "In Review.", "waywiser: Ergonomic methods for assessing spatial models.", "In review at The Journal of Statistical Software", "https://doi.org/10.48550/arXiv.2303.11312",
  "2023", "", "Mahoney, M. J.,", "Johnson, L. K., Silge, J., Frick, H., Kuhn, M., and Beier, C. M. In Review.", "Assessing the performance of spatial cross-validation approaches for models of spatially structured data.", "In review at Environmental Modelling \\& Software", "https://doi.org/10.48550/arXiv.2303.07334"
  ) %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

\vspace{0.4cm}

## Peer-Reviewed Publications

### Journal Articles {.unnumbered}

```{r}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2023", "Johnson, L. K.,", "Mahoney, M. J.,", "Desrochers, M. L., and Beier, C. M. 2023.", "Mapping historical forest biomass for stock-change assessments at parcel to landscape scales", "Forest Ecology and Management, 546, 121348", "https://doi.org/10.1016/j.foreco.2023.121348",
  "2022", "", "Mahoney, M. J.,", "Johnson, L. K., Guinan, A. Z., and Beier, C. M. 2022.", "Classification and mapping of low-statured 'shrubland' cover types in post-agricultural landscapes of the US Northeast.", "The International Journal of Remote Sensing, 43(19-24), 7117-7138", "https://doi.org/10.1080/01431161.2022.2155086",
  "2022", "Johnson, L. K.,", "Mahoney, M. J.,", "Bevilacqua, E., Stehman, S. V., Domke, G. M., and Beier, C. M. 2022.", "Fine-resolution landscape-scale biomass mapping using a spatiotemporal patchwork of LiDAR coverages", "The International Journal of Applied Earth Observation and Geoinformation, 114, 103059", "https://doi.org/10.1016/j.jag.2022.103059",
  "2022", "", "Mahoney, M. J.,", "Johnson, L. K., Bevilacqua, E., and Beier, C. M. 2022.", "Ground noise filtering produces inferior models of forest aboveground biomass.", "GIScience and Remote Sensing, 59(1), 1266-1280", "https://doi.org/10.1080/15481603.2022.2103069",
  "2022", "", "Mahoney, M. J.,", "Beier, C. M., and Ackerman, A. C. 2022.", "unifir: A Unifying API for Interacting with Unity from R.", "Journal of Open Source Software, 7(73), 4388", "https://doi.org/10.21105/joss.04388", 
  "2022", "Tamiminia, H., Salehi, B., Mahdianpari, M., Beier, C. M., Johnson, L. K., Phoenix, D. B., and", "Mahoney, M. J.", "2022.", "Decision tree-based machine learning models for above-ground biomass estimation using multi-source remote sensing data and object-based image analysis.", "Geocarto International", "https://doi.org/10.1080/10106049.2022.2071475",
  "2022", "", "Mahoney, M. J.,", "Beier, C. M., and Ackerman, A. C. 2022.", "terrainr: An R package for creating immersive virtual environments.", "Journal of Open Source Software, 7(69), 4060", "https://doi.org/10.21105/joss.04060",
  "2020", "", "Mahoney, M. J.", "and Stella, J. C. 2020.",
  "Stem size selectivity is stronger than species preferences for beaver, a central place forager.", 
  "Forest Ecology and Management, 475, 118331", "https://doi.org/10.1016/j.foreco.2020.118331",
) %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

### Book Chapters and Conference Proceeding Papers {.unnumbered}

```{r}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  # Add ISBN once it has one
    "2023", "", "Mahoney, M. J.,", "Johnson, L. K., and Beier, C. M. 2023.", "AI for Shrubland Identification and Mapping.", " In: Artificial Intelligence in Earth Science: Best Practices and Fundamental Challenges. (Z. Sun, N. Cristea, P. Rivas, Eds). Elsevier, Amsterdam.", "",
    "2021", "", "Mahoney, M. J.,", "Beier, C. M., and Ackerman, A. C. 2021.", "Interactive landscape simulations for visual resource assessment.", "VRSC 2021 Conference Proceedings", ""
) %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

\newpage{}

# Awards and Honors

```{r}
Awards <- tribble(
  ~ What, ~ When,
  "AGU Outstanding Student Presentation Award", "2023",
  "AGU Student Travel Grant", "2023",
  "US Research Software Engineer Association Travel Award", "2023",
  "STAC Sprint Travel Award", "2023",
  "Outstanding PhD Scholar Award", "2023",
  "Excellence in Academic Research Award", "2023",
  "New York State GIS Association Application Award", "2021",
  "EarthCube AGU Scholarship", "2020",
  "Robin Hood Oak Award for Academic Excellence", "2018",
  "Robert M. Hicks Award for Academic Achievement", "2018",
  "ESF Career Fellowship", "2018",
  "Outstanding Student Award for Accomplishments in Field Ecology and 
  Dendrology", "2017"
)

brief_entries(Awards, What, When)
```

# Fellowships

```{r}
Fellowships <- tribble(
  ~ What, ~ When,
  "Federation of Earth Science Information Partners (ESIP) Community Fellowship - Machine Learning Cluster", "2022-2023", 
)

brief_entries(Fellowships, What, When)
```


```{r, eval=FALSE}
# Grants and Fellowships
# funder, institutional location recieved at, year span
```

# Invited Talks

```{r invited}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2023", "", "Mahoney, M. J.", "", "spatialsample: Infrastructure for spatial cross-validation", "EcoHealth Alliance, New York, NY (Virtual)", "",
  "2023", "", "Mahoney, M. J.", "", "waywiser: An ergonomic toolbox for assesing spatial models", "EcoHealth Alliance, New York, NY (Virtual)", "",
  "2023", "", "Mahoney, M. J.", "", "Making Sausage: How open source scientific software gets made -- and what keeps us from making more", "Federation of Earth Science Information Partners (ESIP) Open Science Cluster (Virtual)", "",
  "2023", "", "Mahoney, M. J.", "", "Mapping shrublands across New York State: Targeted ML for informing management decisions", "Federation of Earth Science Information Partners (ESIP) July Meeting, Burlington, VT", "", 
  "2023", "", "Mahoney, M. J.", "", "Make Reproducibility Easy", "Federation of Earth Science Information Partners (ESIP) January Meeting, Annapolis, MD (Virtual)", "", 
  "2022", "", "Mahoney, M. J.", "", "Building trust in AI outputs: Approaches from NY's forest carbon monitoring program.", "Federation of Earth Science Information Partners (ESIP) July Meeting, Pittsburgh, PA", "",
  "2022", "", "Mahoney, M. J.", "", "Using AI/ML to help New York State manage lands for net zero carbon.", "Federation of Earth Science Information Partners (ESIP) January Meeting, Annapolis, MD (Virtual)", "",
  "2021", "", "Mahoney, M. J.", "", "terrainr: Spatial data access and visualization in R.", "Federation of Earth Science Information Partners (ESIP), Severna Park, MD (Virtual)", "",
  "2021", "Nell, C., ", "Mahoney, M. J.,", "and Platt, L.", "Accessing the USGS National Map and making 3D maps with terrainr.", "USGS Center for Data Integration, Lakewood, CO (Virtual)", "",
  "2021", "", "Mahoney, M. J.", "", "terrainr: Landscape visualizations using data from The National Map.", "USGS National Geospatial Technical Operations Center, Denver, CO (Virtual)", "") %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

# Conference Activity

```{r, eval=FALSE}
# Subheadings: Panels Organized, Papers Presented, Discussant. 
# These entries will include: Name of paper, name of conference, date. 
# Future conferences SHOULD be listed here, if you have had a paper or panel officially accepted.
```

## Sessions Organized

```{r conference_sessions}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2023", "Rao, Y., Sun, Z., Stocks, K.,", "Mahoney, M. J.,", "Redmon, R.", "FAIR for AI in Geoscience: From AI-Ready Data to Practical AI Models", "Session organized at the Federation of Earth Science Information Partners (ESIP) January Meeting, Annapolis, MD (Virtual)", "",
  "2022", "Sun, Z., Ma, M., Burgess, A., Nga, C., Newman, D., Rao, D.,", "Mahoney, M. J.,", "Koren, G., and Kale, A.", "AI for All People: How to Make AI Useful for Earth Science Applications?", "Session organized at the Federation of Earth Science Information Partners (ESIP) July Meeting, Pittsburgh, PA", "",
  "2022", "Sun, Z., Rao, Y.,", "Mahoney, M. J.,", "Lin, C., and Burgess, A.", 'Improving "FAIRness" and "Fairness" of AI/ML in Geoscience.', "Session organized at the Federation of Earth Science Information Partners (ESIP) January Meeting, Annapolis, MD (Virtual)", "") %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

\newpage{}

## Workshops Facilitated

```{r conference_workshops}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2021", "", "Mahoney, M. J.,", "Beier, C. M., and Ackerman, A. C.", "Interactive 3D visualizations of environmental data using the terrainr R package.", "Workshop organized at the Visual Resources Stewardship Conference, Syracuse, NY (Virtual)", "") %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```



## Contributed Talks

```{r}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2023", "", "Mahoney, M. J.", "Ackerman, A. C., and Beier, C. M", "Creating Data-Driven Interactive Virtual Environments for Communicating Forest Change", "American Geophysical Union Fall Meeting, San Francisco, CA", "", 
  "2023", "", "Mahoney, M. J.", "Johnson, L. K., and Beier, C. M", "Consistent Workflows for Assessing Model Performance: Tools and Applications to Natural Climate Solutions", "American Geophysical Union Fall Meeting, San Francisco, CA", "", 
  "2023", "", "Mahoney, M. J.", "", "spatialsample: A tidy approach to spatial cross-validation", "Greater Boston useR Group, Boston, MA", "", 
  "2022", "", "Mahoney, M. J.", "Beier, C. M., and Ackerman, A. C.", "Virtual Environments for Communicating Changing Forests", "Forest Ecosystem Monitoring Collective Conference, Burlington, VT", "", 
    "2022", "Johnson, L. K.,", "Mahoney, M. J.,", "and Beier, C. M.", "A Map-based Stock Change Approach for Fine-scale Biomass and Carbon Accounting in NYS.", "Forest Ecosystem Monitoring Collective Conference, Burlington, VT", "", 
    "2022", "Johnson, L. K.,", "Mahoney, M. J.,", "and Beier, C. M.", "Historical Time Series Biomass Modeling: To Train on Plots or Pixels?", "American Geophysical Union Fall Meeting, Chicago, IL", "",
  "2022", "", "Mahoney, M. J.,", "Johnson, L. K., and Beier, C. M.", "Detecting regenerating forestland at a landscape level", "Ecological Society of America and Canadian Society for Ecology and Evolution Joint Annual Meeting, Montreal, Quebec, Canada", "", 
  "2022", "", "Mahoney, M. J.,", "Beier, C. M., and Ackerman, A. C.", "unifir: A Unifying API for Working with Unity in R", "useR! 2022, Nashville, Tennessee (Virtual)", "", 
  "2022", "", "Mahoney, M. J.,", "Johnson L. K., Bevilacqua E., and Beier C. M.", "Filtering ground noise from LiDAR returns produces inferior models of forest aboveground biomass", "North American Forest Ecology Workshop, Sault Ste Marie, Ontario (Virtual)", "",
  "2022", "", "Mahoney, M. J.", "", "It's not what it looks like: learning to question assumptions when debugging ML models", "Data Mishaps Night, Virtual", "",
  "2021", "Johnson, L. K.,", "Mahoney, M. J.,", "Bevilacqua, E., and Beier, C. M.", "Broad-scale forest biomass mapping: generating contiguous high-resolution predictions using a spatio-temporal patchwork of LiDAR coverages across a mixed-use landscape", "American Geophysical Union Fall Meeting, New Orleans, LA", "",
  "2021", "Johnson, L. K., Beier, C. M., and", "Mahoney, M. J.", "", "Greening Up Before Growing Up: Challenges in Modeling Forest Biomass Recovery Post-Harvest Using Satellite Imagery", "Society of American Foresters National Convention, Virtual", "",
  "2021", "", "Mahoney, M. J.,", "Beier, C. M., and Ackerman, A. C.", "Interactive 3D visualizations of environmental data using the terrainr R package", "Paper presented at the Visual Resources Stewardship Conference, Syracuse, NY (Virtual)", "",
  "2021", "", "Mahoney, M. J., ", "Beier, C. M., and Ackerman, A. C.", "Virtual Environments: Using R as a Frontend for 3D Rendering of Digital Landscapes",  "useR! 2021, Zürich, Switzerland (Virtual)", "",
  "2018", "", "Mahoney, M. J.", " and Stella, J. C. ", "Beaver Foraging Preferences and Impacts on Forest Structure in the Adirondack Mountains of New York", "Forest Ecosystem Monitoring Collective Conference, Burlington, VT", "", 
  "2018", "", "Mahoney, M. J.", " and Stella, J. C. ", "Beaver Foraging Preferences and Impacts on Forest Structure in the Adirondack Mountains of New York", "Rochester Academy of Sciences Fall Scientific Paper Session, Geneseo, NY", "") %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title>. <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

## Poster Presentations

```{r}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2023", "Johnson, L.K.,", "Mahoney, M. J.,", "Domke, G., and Beier, C. M.", "Bridging the Gap Between Pixels and Minimum Estimation Units: Small-Area Uncertainty Estimation with Forest Aboveground Biomass Maps.", "American Geophysical Union Fall Meeting, San Francisco, CA", "",
  "2023", "", "Mahoney, M. J.", "", "Assessing spatial models in scientifically sound ways is hard. New tools for the tidymodels modeling framework can help make it easier.", "Federation of Earth Science Information Partners (ESIP) July Meeting, Burlington, VT", "", 
  "2022", "Woodley, M.", "Mahoney, M. J.,", " Beier, C. M., and Tuttle, S. E.", "Spatiotemporal Dynamics of Snowpack in a Forested Watershed in the Adirondack Mountains, NY", "American Geophysical Union Fall Meeting, Chicago, IL", ""
) %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

\newpage{}

## Poster Presentations (Cont.)

```{r}
tribble(
  ~ When, ~ BeforeYou, ~ You, ~ AfterYou, ~ Title, ~ Details, ~ url,
  "2021", "", "Mahoney, M. J.,", " Johnson, L. K., Bevilacqua, E., and Beier, C. M.", "Filtering ground noise from LiDAR returns produces inferior models of forest aboveground biomass.", "American Geophysical Union Fall Meeting, New Orleans, LA", "",
  "2019", "Dillon, G.,", "Mahoney, M. J.,", "Chase, S., and Johnston, M.", "Nutritional Impacts on Invasive Beech Scale Quantification in Beech Bark Disease Aftermath Forests.", "New York Society of American Foresters Annual Meeting, Syracuse, NY", "",
  "2018", "", "Mahoney, M. J.,", "Zevin, R., and Stella, J.C.", "Impacts of Beaver on Forest Structure and Composition.", "Spotlight on Student Research, Syracuse, NY", "",
  "2018", "", "Mahoney, M. J.,", "Leimanis, V., Desrochers, M. L., Giambona, B., Johnston, M. T., Yanai, R. D., and Dillon, G. A.", "Impacts of Fertilization on Causal Organisms of Beech Bark Disease.", "Spotlight on Student Research, Syracuse, NY", "",
  "2017", "Lasser, G. A., Johnston, M.,", "Mahoney, M.,", "Leimanis, V., and Stoodley, J.", "An Investigation of Nutritional Effects on Beech Bark Disease Causal Organisms.", "Forest Ecosystem Monitoring Collective Conference, Burlington, VT", "",
  "2017", "Lasser, G. A., Johnston, M.,", "Mahoney, M.,", "Leimanis, V., and Stoodley, J.", "An Investigation of Nutritional Effects on Beech Bark Disease Causal Organisms.", "Poster session presented at the Rochester Academy of Sciences Fall Scientific Paper Session, Rochester, NY", ""
) %>% 
  brief_entries(glue::glue("<BeforeYou> \\textbf{<You>} <AfterYou> <Title> <Details>. \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

```{r, eval=FALSE}
# Campus or Departmental Talks
# Invited to give within own department, on own campus
# No guest lectures, that's padding
```

# Research Experience

```{r research}
tribble(
  ~ When, ~ Lab, ~ Role,
  "2020-Present", "Climate And Applied Forest Research Institute (SUNY-ESF)", "Research Assistant"
) %>% 
  brief_entries(glue::glue("\\textbf{<Lab>} \\newline{}<Role>", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

# Teaching Experience

## Graduate Courses

```{r}
tribble(
  ~ When, ~ Title, ~ Role,
  "Fall 2021", "Machine Learning Concepts and Applications", "Instructor of Record"
) %>% 
  brief_entries(glue::glue("\\textbf{<Title>}. <Role>. <When>.", 
                           .open = "<", 
                           .close = ">"),
                .protect = FALSE)
```

## Workshops Facilitated

```{r}
tribble(
  ~ When, ~ Title, ~ Details, ~ url,
  "2023", "Foundations of Scientific Computing", "Mahoney, M. J., Johnson, L. K., and Desrochers, M. L. SUNY-ESF, Syracuse, NY.", "",
  "2023", "Foundational Computing Skills: The Unix Shell, Version Control with Git, and Introduction to R",  "Mahoney, M. J., and Johnson, L. K. SUNY-ESF, Syracuse, NY (Virtual).", "",
  "2021", "Software Carpentry: The Unix Shell, Version Control with Git, and R for Reproducible Scientific Analysis",  "Mahoney, M. J., and Devlin, M.D. SUNY-ESF, Syracuse, NY (Virtual).", "",
) %>% 
  brief_entries(glue::glue("\\textbf{<Title>}. <Details> \\newline \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```



```{r, eval = FALSE}
# Research Experience. 
# RA experience goes here, as well as lab experience.  
# This is one location where slight elaboration is possible, 
# if the research was a team effort on a complex, multi-year theme.  
# One detailed sentence should suffice.  
```

# Service To Profession

```{r}
tribble(
  ~ When, ~ Title, ~ Details, ~ url,
  "2024  - Present", "Associate Editor", "Journal of Open Source Software", "",
  "2023", "Reviewer:", "rOpenSci; PNAS Nexus", "",
  "2022", "Reviewer:", "Journal of Statistical Software; Journal of Open Source Software; 11th International Conference on Climate Informatics.", "",
  "2022 - Present", "Data Carpentry Geospatial Curriculum Advisory Committee.", "Member.", ""
) %>% 
  brief_entries(glue::glue("\\textbf{<Title>} <Details> \\url{<url>}", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```


```{r, eval = FALSE}
# Service To Profession. 
# Include journal manuscript review work (with journal titles 
# [mss. review CAN be given its own separate heading if you do a lot of this work]),
# leadership of professional organizations, etc. 
# Some people put panel organizing under service; check conventions in your field
```

```{r, eval=FALSE}
# Departmental/University Service. Include search committees and other committee work, appointments to Faculty Senate, etc.  Sorry to be a pain, but here the convention is that the Title or Committee is left justified, with the year in the entry.  Don’t ask me why, and only a convention, not a strict rule
```

```{r, eval = FALSE}
# Extracurricular University Service. [Optional. ] Can include involvement in student groups, sporting clubs, etc.
```

\newpage{}

# Non-Academic Experience

```{r}
# Community Involvement/Outreach. [Optional.]  This includes work with libraries and schools, public lectures, etc.
tribble(
  ~ When, ~ Group, ~ Role, ~ Details,
  "2023", "Permian Global Research Limited",
  "Data Scientist (Consultant)",
  "Consultant (full-time equivalent) with Permian Global's research arm, working on tool development enabling teams to download spatial data, fit biomass and carbon models, predict large footprints, and assess results. Transformed multi-week modeling workflows into hours-long processes. Assisted with field sample design and model architecture reviews.",
  "2022", "RStudio PBC.", 
  "Open Source Engineering Intern", 
  "Intern with RStudio's tidymodels team, working on the R packages 'spatialsample' for spatial cross-validation, 'rsample' for resampling and cross-validation, 'waywiser' for measuring spatial autocorrelation in model residuals, and 'applicable' for calculating model applicability domains."
) %>% 
  brief_entries(glue::glue(" \\textbf{<Group>} <Role>. \\newline{} <Details>",
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```


# Community Involvement and Outreach

```{r}
# Community Involvement/Outreach. [Optional.]  This includes work with libraries and schools, public lectures, etc.
tribble(
  ~ When, ~ Group, ~ Role, ~ Details,
  "2019-2020", "Code for Boston - Clean Slate Project.", 
  "Data Scientist and Project Manager (Volunteer)", 
  "Project working with Greater Boston Legal Society to advance criminal justice reform efforts."
) %>% 
  brief_entries(glue::glue(" \\textbf{<Group>} <Role>. \\newline{} <Details>",
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

```{r, eval = FALSE}
# Media Coverage. [Optional.] Coverage of your work by the media.
```

# Software Development

```{r packages}
tribble(
  ~ Pkg, ~ When, ~ Role, ~ Details,
  "waywiser", "2022", "Lead developer", "Infrastructure for assessing spatial autocorrelation in model residuals",
  "rsample", "2022", "Developer", "Data resampling infrastructure for model evaluation",
  "geojsonio", "2022", "Maintainer", "Utility to convert geographic data to GeoJSON and TopoJSON formats",
  "spatialsample", "2022", "Developer, Maintainer", "Functions for spatial resampling with the 'rsample' package", 
  "unifir", "2022", "Lead developer", "A Unifying API for working with Unity in R",
  "terrainr", "2021", "Lead developer", "Retrieve Data from the USGS National 
  Map and Transform it for 3D Landscape Visualizations.",
  "heddlr", "2020", "Lead developer", "Tools to enable functional programming 
  workflows for dynamic R Markdown document generation.",
  "spacey", "2020", "Lead developer", "USGS and ESRI data access for beautiful 
  landscape visualization."
) %>% 
  brief_entries(glue::glue("\\textbf{<Pkg>}: <Role> \\newline <Details>", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```

# Affiliations

```{r affiliations}
# Professional Memberships/Affiliations. 
# All professional organizations of which you are a member listed vertically. 
# Include years of joining when you are more senior and those years recede into the past—demonstrates length of commitment to a field.

tribble(
  ~ When, ~ What, ~Who,
  "2021 - Present", "The Carpentries", "Instructor in good standing.",
  "2021 - Present", "American Geophyiscal Union", "Member.",
  "2021 - Present", "NYS GIS Association", "Member.",
  "2019 - Present", "Data Visualization Society", "Member."
) %>% 
  brief_entries(glue::glue("\\textbf{<What>}. <Who>", 
                           .open = "<", 
                           .close = ">"), 
                When, 
                .protect = FALSE)
```


```{r, eval=FALSE}
# References
# List references vertically. Give name and full title. 
# Do not refer to references as “Dr. xxx,” or “Professor xxx.” This makes you look like a graduate student. 
# Give full snail mail contact information along with tel and email. 
# To do otherwise is amateurish, even though we know nobody is going to use the snail mail address. 
# Do not give narrative verbiage or explanation of these references (ie, “Ph.D. Committee member,” etc.). 
# The only exception is a single reference that may be identified as “Teaching Reference.” This would be the fourth of four references.
```

